---
title       : HTMN
subtitle    : 
author      : 
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

```{r, include=FALSE}
library(DataComputing)
library(lubridate)
library(reshape2)
library(ggthemes)
library(RColorBrewer)
library(grid)
library(scales)

library(car)
library(dplyr)

#library(printr)
library(rvest)
library(ggrepel)
library(stargazer)
library(lfe)
```

```{r include=FALSE}

#Hope's Case Study: Bay Area Counties vs Los Angeles County, who is doing their part?

water_residential <- "uw_supplier_data040416.csv"
new_water_residential <- water_residential  %>%
  read.file() %>%
  select(Supplier.Name, Stage.Invoked, Mandatory.Restrictions, 
         Reporting.Month, CALCULATED.R.GPCD.Reporting.Month..Values.calculated.by.Water.Board.staff.using.methodology.available.at.http...www.waterboards.ca.gov.waterrights.water_issues.programs.drought.docs.ws_tools.guidance_estimate_res_gpcd.pdf., Hydrologic.Region, Penalties.Assessed, X..Residential.Use)

names(new_water_residential)[names(new_water_residential) == 'CALCULATED.R.GPCD.Reporting.Month..Values.calculated.by.Water.Board.staff.using.methodology.available.at.http...www.waterboards.ca.gov.waterrights.water_issues.programs.drought.docs.ws_tools.guidance_estimate_res_gpcd.pdf.'] <- 'resid_use'

new_water_residential$Reporting.Month <- new_water_residential$Reporting.Month%>%
  mdy()

#los angeles water suppliers
#want all of los angeles county so any water supplier that matches the cities within LA county
#some gsub to get this nice list of the cities in LA county

lacities <- "Agoura Hills Alhambra Arcadia Artesia Avalon Azusa Baldwin Park Bell Bell Gardens Bellflower Beverly Hills Bradbury Burbank Calabasas Carson Cerritos Claremont Commerce Compton Covina Cudahy Culver City Diamond Bar Downey Duarte El Monte El Segundo Gardena Glendale Glendora Hawaiian Gardens Hawthorne Hermosa Beach Hidden Hills Huntington Park Industry Inglewood Irwindale La Cañada Flintridge La Habra Heights La Mirada La Puente La Verne Lakewood Lancaster Lawndale Lomita Long Beach Los Angeles Lynwood Malibu Manhattan Beach Maywood Monrovia Montebello Monterey Park Norwalk Palmdale Palos Verdes Estates Paramount Pasadena Pico Rivera Pomona Rancho Palos Verdes Redondo Beach Rolling Hills Rolling Hills Estates Rosemead San Dimas San Fernando San Gabriel San Marino Santa Clarita Santa Fe Springs Santa Monica Sierra Madre Signal Hill South El Monte South Gate South Pasadena Temple City Torrance Vernon Walnut West Covina West Hollywood Westlake Village Whittier"
lacities <- gsub(" " , ")|(" , lacities)

lacities

#NOT SHOWN:then manually put a . in between cities with more than one word in the name to account for spaces
#below is the dataset that only has los angeles county levels of water usage

losangeles.avg <- new_water_residential%>%
  filter(grepl("(Agoura.Hills)|(Alhambra)|(Arcadia)|(Artesia)|(Avalon)|(Azusa)|(Baldwin.Park)|(Bell)|(Bell.Gardens)|(Bellflower)|(Beverly.Hills)|(Bradbury)|(Burbank)|(Calabasas)|(Carson)|(Cerritos)|(Claremont)|(Commerce)|(Compton)|(Covina)|(Cudahy)|(Culver.City)|(Diamond.Bar)|(Downey)|(Duarte)|(El.Monte)|(El.Segundo)|(Gardena)|(Glendale)|(Glendora)|(Hawaiian)|(Gardens)|(Hawthorne)|(Hermosa.Beach)|(Hidden.Hills)|(Huntington.Park)|(Industry)|(Inglewood)|(Irwindale)|(La.Cañada.Flintridge)|(La.Habra.Heights)|(La.Mirada)|(La.Puente)|(La.Verne)|(Lakewood)|(Lancaster)|(Lawndale)|(Lomita)|(Long.Beach)|(Los.Angeles)|(Lynwood)|(Malibu)|(Manhattan.Beach)|(Maywood)|(Monrovia)|(Montebello)|(Monterey.Park)|(Norwalk)|(Palmdale)|(Palos.Verdes.Estates)|(Paramount)|(Pasadena)|(Pico.Rivera)|(Pomona)|(Rancho)|(Palos.Verdes)|(Redondo.Beach)|(Rolling.Hills)|(Rolling.Hills.Estates)|(Rosemead)|(San.Dimas)|(San.Fernando)|(San.Gabriel)|(San.Marino)|(Santa.Clarita)|(Santa.Fe.Springs)|(Santa.Monica)|(Sierra.Madre)|(Signal.Hill)|(South.El.Monte)|(South.Gate)|(South.Pasadena)|(Temple.City)|(Torrance)|(Vernon)|(Walnut)|(West.Covina)|(West.Hollywood)|(Westlake)|(Village)|(Whittier)", Supplier.Name))%>%
  group_by(Reporting.Month)%>%
  summarise(la_use_avg = mean(resid_use))

#there are multiple counties surrounding the bay: SF, Marin, Sonoma, Napa, Solano, Contra Costa, Alameda, Santa Clara, and San Mateo. Eastbay

sfbay <- "Alameda, California
+ Albany, California
+ American Canyon, California
+ Antioch, California
+ Atherton, California
+ B
+ Belmont, California
+ Belvedere, California
+ Benicia, California
+ Berkeley, California
+ Brentwood, California
+ Brisbane, California
+ Burlingame, California
+ C
+ Calistoga, California
+ Campbell, California
+ Clayton, California
+ Cloverdale, California
+ Colma, California
+ Concord, California
+ Corte Madera, California
+ Cotati, California
+ Cupertino, California
+ D
+ Daly City, California
+ Danville, California
+ Dixon, California
+ Dublin, California
+ E
+ East Palo Alto, California
+ El Cerrito, California
+ Emeryville, California
+ F
+ Fairfax, California
+ Foster City, California
+ Fremont, California
+ G
+ Gilroy, California
+ H
+ Half Moon Bay, California
+ Hayward, California
+ Healdsburg, California
+ Hercules, California
+ Hillsborough, California
+ L
+ Lafayette, California
+ Larkspur, California
+ Livermore, California
+ Los Altos, California
+ Los Altos Hills, California
+ Los Gatos, California
+ M
+ Martinez, California
+ Menlo Park, California
+ Mill Valley, California
+ Millbrae, California
+ Milpitas, California
+ Monte Sereno, California
+ Moraga, California
+ Morgan Hill, California
+ Mountain View, California
+ N
+ Napa, California
+ Newark, California
+ Novato, California
+ O
+ Oakland, California
+ Oakley, California
+ Orinda, California
+ P
+ Pacifica, California
+ Palo Alto, California
+ Petaluma, California
+ Piedmont, California
+ Pinole, California
+ Pittsburg, California
+ Pleasant Hill, California
+ Pleasanton, California
+ Portola Valley, California
+ R
+ Redwood City, California
+ Richmond, California
+ Rio Vista, California
+ Rohnert Park, California
+ Ross, California
+ S
+ St. Helena, California
+ San Anselmo, California
+ San Carlos, California
+ San Francisco
+ San Jose, California
+ San Leandro, California
+ San Mateo, California
+ San Pablo, California
+ San Rafael, California
+ San Ramon, California
+ Santa Clara, California
+ Santa Rosa, California
+ Saratoga, California
+ Sausalito, California
+ Sebastopol, California
+ Sonoma, California
+ South San Francisco, California
+ Suisun City, California
+ Sunnyvale, California
+ T
+ Tiburon, California
+ U
+ Union City, California
+ V
+ Vacaville, California
+ Vallejo, California
+ W
+ Walnut Creek, California
+ Windsor, California
+ Woodside, California
+ Y
+ Yountville, California"

sfbay <- gsub("California", "", sfbay) #get rid of california
sfbay <- gsub("\n[A-Z]\n", "", sfbay) #get rid of the headers for each section of cities beginning with a certain letter
sfbay <- gsub("\n", "", sfbay) #getting rid of extra newlines
sfbay <- gsub(", " , ")|(", sfbay) #inputting the separations for when I use grepl later

sfbay  #want to look at it so I can copy/paste and make small edits for when I use it in grepl


bayavg <-  new_water_residential%>%
  filter(grepl( "(Alameda)|(Albany)|(American.Canyon)|(Antioch)|(Atherton)|(Belmont)|(Belvedere)|(Benicia)|(Berkeley)|(Brentwood)|(Brisbane)|(Burlingame)|(Calistoga)|(Campbell)|(Clayton)|(Cloverdale)|(Colma)|(Concord)|(Corte.Madera)|(Cotati)|(Cupertino)|(Daly.City)|(Danville)|(Dixon)|(Dublin)|(East.Palo.Alto)|(El.Cerrito)|(Emeryville)|(Fairfax)|(Foster.City)|(Fremont)|(Gilroy)|(Half.Moon.Bay)|(Hayward)|(Healdsburg)|(Hercules)|(Hillsborough)|(Lafayette)|(Larkspur)|(Livermore)|(Los.Altos)|(Los.Altos.Hills)|(Los.Gatos)|(Martinez)|(Menlo.Park)|(Mill.Valley)|(Millbrae)|(Milpitas)|(Monte.Sereno)|(Moraga)|(Morgan.Hill)|(Mountain.View)|(Napa)|(Newark)|(Novato)|(Oakland)|(Oakley)|(Orinda)|(Pacifica)|(Palo.Alto)|(Petaluma)|(Piedmont)|(Pinole)|(Pittsburg)|(Pleasant.Hill)|(Pleasanton)|(Portola.Valley)|(Redwood.City)|(Richmond)|(Rio.Vista)|(Rohnert.Park)|(Ross)|(St..Helena)|(San.Anselmo)|(San.Carlos)|(San.FranciscoSan.Jose)|(San.Leandro)|(San.Mateo)|(San.Pablo)|(San.Rafael)|(San.Ramon)|(Santa.Clara)|(Santa.Rosa)|(Saratoga)|(Sausalito)|(Sebastopol)|(Sonoma)|(South.San.Francisco)|(Suisun.City)|(Sunnyvale)|(Tiburon)|(Union.City)|(Vacaville)|(Vallejo)|(Walnut.Creek)|(Windsor)|(Woodside)|(Yountville)|(East.Bay)", Supplier.Name ))%>%
  group_by(Reporting.Month)%>%
  summarise(bay_use_avg = mean(resid_use))

# we want to compare to california as a whole so let's take the average for every month for the whole state!

state.avg <- new_water_residential%>%
  group_by(Reporting.Month)%>%
  summarise(state_use_avg = mean(resid_use))

# Now let's combine all three of these datasets so that we have just one dataset we're plotting from

la_state <- state.avg%>%
  inner_join(losangeles.avg, by = c("Reporting.Month" = "Reporting.Month"))

alljoined <- la_state%>%
  inner_join(bayavg, by = c("Reporting.Month" = "Reporting.Month"))

#now that I have everything joined, I have to make it tidy
#using gather to make it narrow

narrowall <- alljoined%>%
  gather(key = boundary, value = avg_resid_use, state_use_avg, la_use_avg, bay_use_avg)

narrowall$boundary <- gsub("state_use_avg", "California", narrowall$boundary)

narrowall$boundary <- gsub("la_use_avg", "Los Angeles County", narrowall$boundary)

narrowall$boundary <- gsub("bay_use_avg", "All 9 Bay Area Counties", narrowall$boundary)
```


```{r, include=FALSE}
#PLOTPLOTPLOTPLOTPLOT HOPE CASE STUDY
  ggplot(narrowall, aes(x=Reporting.Month, y= avg_resid_use, color = boundary)) +
  geom_point() + 
  stat_smooth(se=FALSE, method="loess") +
  labs(x = "Month", y = "Average Residential Water Usage", title = "Average Residential Water Usage vs Month") +
  theme(legend.key = element_rect(colour = "black"),
        plot.background = element_rect(colour = "grey"),
        panel.background = element_rect(fill = "grey"),
        panel.background = element_rect(color = "black"),
        panel.grid.minor = element_line(linetype = "dotted"), 
        axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.0)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(2))
        ) + geom_vline(aes(xintercept = as.numeric(ymd("2015-04-01"))), color = "red", size=1.5) +
  scale_colour_manual("Region", values = c("green", "blue","yellow"))
```

```{r, include=FALSE}
#Hope's Map

#install.packages("mapdata")
#install.packages("ggmap")
library(mapdata)
library(ggmap)

#data set that has drought by county

drought_severity <- "final_COUNTY2000-2016.csv"
drought_severity <- drought_severity%>%
  read.file()
drought_severity$county <- gsub(" County", "", drought_severity$county)
drought_severity$county <- sapply(drought_severity$county, tolower)

names(drought_severity)[names(drought_severity) == "county"] <- "subregion"
drought_severity <- data.frame(drought_severity)

#adding month and year column for later
drought_severity$releaseDate <- as.Date(drought_severity$releaseDate)
drought_severity$month <- months(drought_severity$releaseDate, abbr = TRUE)
drought_severity$year <- year(ymd(drought_severity$releaseDate)) 

#narrow version of drought_severity 
#taking the average for each month for each category of severity for simplicity

tidy_severity <- drought_severity%>%
  gather(key = category, value = value, NONE, D0, D1, D2, D3, D4)%>%
  select(subregion, month, year, category, value, FIPS)%>%
    group_by(month, year, subregion, category)%>%
  summarise(ave_value = mean(value))

#just making sure everything is in the correct format for ease of plotting
tidy_severity <- data.frame(tidy_severity)
tidy_severity$year <- as.numeric(tidy_severity$year)


#coordinates for the california counties
CAcounties <- map_data('county')%>%
  filter(region == "california")
CAcounties <- data.frame(CAcounties)


#merge drought information with coordinates for each county
CAcountiesvalues <- CAcounties%>%
  right_join(tidy_severity, by = "subregion")


#creating levels for mapping later
CAcountiesvalues$category <- factor(CAcountiesvalues$category, levels = c("D4", "D3", "D2", "D1", "D0", "NONE"))

CAcountiesvalues$month <- factor(CAcountiesvalues$month, levels = c("January", "February", "March", "April", "May","June", "July", "August","September", "October", "November","December"))

#okay so this makes the really large grid with many maps, may just use this as an overview, then take pieces from it?

CAcountiesvalues%>% 
  ggplot() + 
  geom_polygon(aes (x = long, y = lat, group = group, fill = ave_value), colour = "white", size = 0.02)+ scale_fill_gradient(low = "yellow", high = "red") + 
  facet_grid(category ~ year) +
  labs(x = "Year", y = "Drought Severity", title = "Drought Severity vs Year") +
  theme(axis.line=element_blank(),axis.text.x=element_blank(),axis.text.y=element_blank(),axis.ticks=element_blank())

timelapse <- "final_COUNTY2000-2016.csv"
timelapse <- timelapse  %>%
  read.file() %>%
  select(releaseDate, county, FIPS, NONE, D0, D1, D2, D3, D4)

bins <- timelapse %>% mutate(D0=D0-D1, D1=D1-D2, D2=D2-D3, D3=D3-D4)

bins$releaseDate <- as.Date(bins$releaseDate)
bins$month <- months(bins$releaseDate)
bins$year <- year(ymd(bins$releaseDate)) 

bins <- bins %>% mutate( FIPS_avg = (1*D0 + 2*D1 + 3*D2 + 4*D3 + 5*D4) /100 - 1) %>% group_by(month, year, FIPS, county) %>% summarise(monthly_avg = round(mean(FIPS_avg)))

bins$county <- gsub(" County", "", bins$county)
bins$county <- sapply(bins$county, tolower)

names(bins)[names(bins) == "county"] <- "subregion"
bins<- data.frame(bins)

drought_levels <- function(x) {
         (
          if (x==-1) {
            "No Drought (NONE)"
          } else if (x==0) {
            "Abnormally Dry (D0)"
          } else if (x==1) {
            "Moderate Drought (D1)"
          } else if (x==2) {
            "Severe Drought (D2)"
          } else if (x==3) {
            "Extreme Drought (D3)"
          } else
            "Exceptional Drought (D4)"
         )
}

bins <- bins %>% mutate(monthly_avg=sapply(monthly_avg,drought_levels))

binscounties <- bins%>%
  right_join(CAcounties, by = c("subregion"))

binscounties$month <- factor(binscounties$month, levels = c("January", "February", "March", "April", "May","June", "July", "August","September", "October", "November","December"))

binscounties$monthly_avg <- factor(binscounties$monthly_avg, levels = c("No Drought (NONE)", "Abnormally Dry (D0)", "Moderate Drought (D1)", "Severe Drought (D2)", "Extreme Drought (D3)", "Exceptional Drought (D4)"))

binscounties <- binscounties %>%
  group_by(year)%>%
  arrange(month)%>%
  mutate(completedate = (paste(month, year)))

months <- c("January", "February", "March", "April", "May","June", "July", "August","September", "October", "November","December")

months <- rep(months, times = 17)

years <- rep(2000:2016, each = 12)

monthsyears <- paste(months, years)

monthsyears <- monthsyears[1:(length(monthsyears) - 8)]

monthsyears

binscounties$completedate <- factor(levels = c(monthsyears), binscounties$completedate)


binscounties$completedate <- as.factor( binscounties$completedate)

binscounties <- data.frame(binscounties)
```

```{r, include=FALSE}
#Tiffany's Graph

timelapse <- "final_COUNTY2011-2016.csv"
timelapse <- timelapse  %>%
  read.file() %>%
  select(releaseDate, FIPS, NONE, D0, D1, D2, D3, D4)

bins <- timelapse %>% mutate(D0=D0-D1, D1=D1-D2, D2=D2-D3, D3=D3-D4, releaseDate = floor_date(lubridate::ymd(releaseDate), "month"))

names(bins)[1] <- "Month"

bins <- bins %>% mutate( FIPS_avg = (1*D0 + 2*D1 + 3*D2 + 4*D3 + 5*D4) /100 - 1) %>% group_by(Month, FIPS) %>% summarise(monthly_avg = round(mean(FIPS_avg)))

drought_levels <- function(x) {
         (
          if (x==-1) {
            "No Drought (NONE)"
          } else if (x==0) {
            "Abnormally Dry (D0)"
          } else if (x==1) {
            "Moderate Drought (D1)"
          } else if (x==2) {
            "Severe Drought (D2)"
          } else if (x==3) {
            "Extreme Drought (D3)"
          } else
            "Exceptional Drought (D4)"
         )
}

bins <- bins %>% mutate(monthly_avg=sapply(monthly_avg,drought_levels))

bins$monthly_avg <- factor(bins$monthly_avg, levels = c("No Drought (NONE)", "Abnormally Dry (D0)", "Moderate Drought (D1)", "Severe Drought (D2)", "Extreme Drought (D3)", "Exceptional Drought (D4)"))

bins <- bins %>% select(Month, monthly_avg)  %>% arrange(Month)
```

```{r, include=FALSE}
#Noosha's Graphs

water_residential <- "uw_supplier_data040416.csv"
water_residential <- water_residential  %>%
  read.file() %>%
  select(Supplier.Name, Stage.Invoked, Mandatory.Restrictions, Reporting.Month, CALCULATED.R.GPCD.Reporting.Month..Values.calculated.by.Water.Board.staff.using.methodology.available.at.http...www.waterboards.ca.gov.waterrights.water_issues.programs.drought.docs.ws_tools.guidance_estimate_res_gpcd.pdf., Hydrologic.Region, Penalties.Assessed, X..Residential.Use, Water.Days.Allowed.Week, Conservation.Standard..starting.in.June.2015.) %>% 
  mutate(reporting_month = lubridate::mdy(Reporting.Month), 
         policy_enacted = ifelse(reporting_month < as.numeric(ymd("2015-04-15")), 0, 1),
         state_mandatory_restrictions = ifelse(policy_enacted == 1, "After \nState Restrictions", "Before \nState Restrictions"),
    month_dummies = ifelse(reporting_month %in% ymd(c("2014-06-15", "2015-06-15")), 6, 
                    ifelse(reporting_month %in% ymd(c("2014-07-15", "2015-07-15")), 7,
                    ifelse(reporting_month %in% ymd(c("2014-08-15", "2015-08-15")), 8,
                    ifelse(reporting_month %in% ymd(c("2014-09-15", "2015-09-15")), 9,
                    ifelse(reporting_month %in% ymd(c("2014-10-15", "2015-10-15")), 10,
                    ifelse(reporting_month %in% ymd(c("2014-11-15", "2015-11-15")), 11,
                    ifelse(reporting_month %in% ymd(c("2015-12-15", "2016-12-15")), 12,
                    ifelse(reporting_month %in% ymd(c("2015-01-15","2016-01-15")), 1,
                    ifelse(reporting_month %in% ymd(c("2015-02-15","2016-02-15")), 2,                      ifelse(reporting_month == ymd(c("2015-03-15")), 3,                                     ifelse(reporting_month == ymd(c("2015-04-15")), 4, 5))))))))))))        
water_residential$state_mandatory_restrictions <- factor(water_residential$state_mandatory_restrictions, levels = c("Before \nState Restrictions", "After \nState Restrictions"))
  
names(water_residential)[names(water_residential) == 'CALCULATED.R.GPCD.Reporting.Month..Values.calculated.by.Water.Board.staff.using.methodology.available.at.http...www.waterboards.ca.gov.waterrights.water_issues.programs.drought.docs.ws_tools.guidance_estimate_res_gpcd.pdf.'] <- 'resid_use'
```

```{r, include=FALSE}
#Noosha's analysis regression 1
fixed <- felm(resid_use ~ policy_enacted | Supplier.Name + month_dummies, data=water_residential)
```

```{r, include=FALSE}
#Noosha's analysis regression 2
month_water_residential <- water_residential  %>%
  mutate(overtime_use = ifelse(resid_use <= 100.00, "0-100",
                    ifelse(resid_use <= 200.00, "101-200",                                                 ifelse(resid_use <= 300.00, "201-300",
                     ifelse(resid_use <= 400.00, "301-400",
                        "400+"))))) %>%
  group_by(overtime_use, reporting_month, month_dummies) %>%
  summarise(total = n())
```

```{r, include=FALSE}
#Megan's graph

usage <- "usagedataset.csv"
table <- usage %>%
  read.file() %>%
  select(Supplier_Name,ResUse, Penalties_Assessed, Reporting_Month, Percent_ResUse, Mandatory_Restrictions,ReportedProd, Prod13, CS) %>%
  filter( CS != "NULL") %>%
  mutate(date = lubridate::mdy(Reporting_Month),
         
 norcal = ifelse(Supplier_Name %in% c("Pleasanton  City of","Santa Cruz  City of","East Bay Municipal Utilities District", "Yuba City  City of", "Hillsborough  Town of", "Sacramento Suburban Water District", "Olivehurst Public Utility District", "Alco Water Service"), 1,0), 

socal= ifelse(Supplier_Name %in% c("Newport Beach  City of", "Beverly Hills  City of", "Castaic Lake Water Agency Santa Clarita Water Division", "Montecito Water District", "Ontario  City of", "Triunfo Sanitation District / Oak Park Water Service",  "Arroyo Grande  City of" , "South Coast Water District"), 1,0),     
cv = ifelse(Supplier_Name %in% c("Clovis  City of",  "Fresno  City of" ,  "Ceres  City of", "Hanford  City of",  "Tulare, City of", "Turlock  City of ", "Los Banos, City of", "Exeter  City of"), 1, 0),
Month = month(date))

table <- table %>%
  mutate(I_Prod = as.numeric(gsub(",", "", table$Prod13)),F_Prod = as.numeric(gsub(",", "", table$ReportedProd)),   
Standard = as.numeric(gsub("%", "", table$CS)))

NC <- c("Pleasanton  City of", "Santa Cruz  City of", "East Bay Municipal Utilities District","Yuba City  City of", "Hillsborough  Town of", "Sacramento Suburban Water District", "Olivehurst Public Utility District", "Alco Water Service")

NCT <- table %>%
  filter(Supplier_Name %in% NC) %>%
  mutate(Year= year(date), Month = month(date)) %>%
  filter (Year == 2015) %>%
  filter (Penalties_Assessed > 0) 
```

```{r, include=FALSE}

# Megan's graph ( I think thisis for Central Valley?)
CV <- c("Clovis  City of", "Fresno  City of", "Ceres  City of", "Hanford  City of", "Tulare, City of", "Turlock  City of", "Los Banos, City of", "Exeter  City of")

CVT <- table %>%
  filter(Supplier_Name %in% CV) %>%
  mutate(Year= year(date)) %>%
  mutate(Month = month(date)) %>%
  filter (Year == 2015) %>%
  filter (Penalties_Assessed > 0)

```

```{r, include=FALSE}
# Megan's graph (Southern CA)
SC<- c("Newport Beach  City of", "Beverly Hills  City of","Castaic Lake Water Agency Santa Clarita Water Division" ,"Montecito Water District", "Ontario  City of", "Triunfo Sanitation District / Oak Park Water Service", "Arroyo Grande  City of", "South Coast Water District")

SCT <- table %>%
  filter(Supplier_Name %in% SC) %>%
  mutate(Year= year(date)) %>%
  mutate(Month = month(date)) %>%
  filter (Year == 2015) %>%
  filter (Penalties_Assessed > 0) 
```

```{r, include=FALSE}

#Megan's last graph

CONS <- table %>%
  select(Supplier_Name, I_Prod, F_Prod, Standard, date) %>%
  mutate(Year= year(date)) %>%
  filter(Year == 2015 | Year == 2016) %>%
  filter(Standard != "NULL") %>%
  mutate(Month= month(date)) %>%
  mutate(Change = ((I_Prod-F_Prod)/(I_Prod)) *100, 
         pc= ifelse(Change > Standard, 1, 0),
         met =ifelse(pc == 1, "Met", "Did not Meet")) %>%
  group_by(met, date) %>%
  summarise(total = n())

month_named <- c(
  '2015-06-15'= "June 2015",
  '2015-07-15'= "July 2015",
  '2015-08-15'= "August 2015",
  '2015-09-15'= "September 2015", 
  '2015-10-15'= "October 2015",
  '2015-11-15'= "November 2015",
  '2015-12-15'= "December 2015",
  '2016-01-15'= "January 2016",
  '2016-02-15'= "February 2016")
```

```{r, include=FALSE}
#Megan's last analysis
REGC <- table %>%
  select(Supplier_Name, I_Prod, F_Prod, Standard, date) %>%
  mutate(Year= year(date)) %>%
  filter(Year == 2015 | Year == 2016) %>%
  filter(Standard != "NULL") %>%
  mutate(Month= month(date)) %>%
  mutate(Change = ((I_Prod-F_Prod)/(I_Prod)) *100)

linear <- lm(Change~Standard + I_Prod,data = REGC) 
summary(linear)
```

--- &twocol

## HTMN: The California Drought & Residential Water Usage 

**Question 1: How have CA drought conditions changed since the drought started in 2011?**

<!-- Limit image width and height -->
<style type="text/css">
img {     
  max-height: 560px;     
  max-width: 964px; 
}
</style>
 
<!-- Center image on slide -->
<script type="text/javascript" src="http://ajax.aspnetcdn.com/ajax/jQuery/jquery-1.7.min.js"></script>
<script type="text/javascript">
$(function() {     
  $("p:has(img)").addClass('centered'); 
});
</script>

*** =left 
```{r, echo=FALSE, fig.width=5.5, fig.height=6, warning=FALSE}
bins %>% ggplot(aes(x=Month, fill=monthly_avg)) + geom_bar() + 
 scale_fill_manual("Drought Severity", values=c("#7baad8", "#fffc67", "orange", "darkorange3", "orangered3", "firebrick4")) + facet_wrap(~ monthly_avg) + ggtitle("Number of Counties in \nEach Severity Level") + ylab("Number of Counties") + theme(axis.text.x = element_text(angle = 45, hjust = 1)) + theme(panel.background = element_rect(fill = "grey"),
        panel.background = element_rect(color = "black"),
        panel.grid.minor = element_line(linetype = "dotted"), 
        axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.0)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.8)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  guides(fill=F)
```

*** =right
```{r, fig.width=9, fig.height=7, echo=FALSE, warning=FALSE}
binscounties%>%
  filter(year >= 2011)%>%
  ggplot() + 
  geom_polygon(aes (x = long, y = lat, group = group, fill = monthly_avg), colour = "white", size = 0.02)+
  facet_wrap(~completedate, ncol = 8, drop = TRUE) +
  labs(x = "Month", y = "Year", title = "Drought Severity from 2011-Present") +
  theme(axis.line=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        panel.grid.major = element_blank(),	
        panel.grid.minor = element_blank(), 
        legend.key = element_rect(colour = "black"),
        plot.background = element_rect(colour = "grey"),
        panel.background = element_rect(fill = "grey"),
        panel.background = element_rect(color = "black"),
        panel.grid.minor = element_line(linetype = "dotted"), 
        axis.title = element_text(size = rel(1.5)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.8))
        ) + 
  theme(axis.line=element_blank(),axis.text.x=element_blank(),axis.text.y=element_blank(),axis.ticks=element_blank()) + 
 scale_fill_manual("Drought Severity", values=c("#7baad8", "#fffc67", "orange", "darkorange3", "orangered3", "firebrick4"))

```

--- &twocol 

**Question 2: How has residential water usage changed since the enactment of the statewide mandatory reductions in April 2015?**

*** =left width:70%
```{r, echo=FALSE, fig.width=7, fig.height=5, warning=FALSE}
#top left
water_residential %>% 
  ggplot(aes(x=reporting_month, y= resid_use)) +
  geom_point() + 
  geom_jitter() +
  geom_vline(aes(xintercept = as.numeric(ymd("2015-04-01"))), color = "red", size=1.5) +
  xlab("Reported Months") +
  ylab("Residential Water Usage \n(Gallons-per-Capita-per-Day)") +
  ggtitle("2014-2016 Reported California Residential Water Usage") +
  geom_smooth() +
  theme(panel.background = element_rect(fill = "grey"),
        axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(1.0)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.5)))
```

```{r, results='asis', warning=FALSE, echo=FALSE, fig.width=4, fig.height=1}
#top right
stargazer(fixed, type="html", omit = NULL, dep.var.labels=c("Residential Water Usage (R-GPCD)"), out="noosha_models.htm")
```

***=right width:30%

```{r, echo=FALSE, warning=FALSE, fig.width=7, fig.height=5}

#bottom left

month_water_residential %>% 
  ggplot(aes(x=reporting_month, y = total, group =  overtime_use, fill=overtime_use, color = overtime_use )) +
  geom_bar(stat="identity", position="identity") +
  geom_line(size = 1) +
  scale_fill_manual(name="Residental Usage\n(Gallons-per-\nCapita-per-Day)",
                    values=c("#08519C", "#3182BD", "#6BAED6", "#6a51a3", "#ae017e"),
                    breaks=c("0-100", "101-200", "201-300", "301-400", "400+"),
                    labels=c("0-100", "101-200", "201-300","301-400", "400+")) +
  geom_vline(aes(xintercept = as.numeric(ymd("2015-04-01"))), color = "red", size=1.5) +
  scale_colour_manual(name="Residental Usage\n(Gallons-per-\nCapita-per-Day)",
                    values=c("#08519C", "#3182BD", "#6BAED6", "#6a51a3", "#ae017e"),
                    breaks=c("0-100", "101-200", "201-300", "301-400", "400+"),
                    labels=c("0-100", "101-200", "201-300","301-400", "400+")) +
  geom_label_repel(
    data = subset(month_water_residential, reporting_month %in% ymd(c("2014-06-15", "2015-04-15","2016-02-15"))),
    aes(label = total),
    size = 6, color = "white",
    fontface = 'bold',
    box.padding = unit(0.25, "lines"),
    point.padding = unit(0.25, "lines"),
    show.legend=FALSE) + 
 theme(panel.background = element_rect(fill = "grey"),
        axis.title = element_text(size = rel(1.5)),
        axis.text = element_text(size = rel(.9)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.5)),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank()) +
  ylab("Number of Water Supplier Agencies") +
  xlab("Reported Months") +
  ggtitle("2014-2016 Reported California Residential Water \nUsage by Number of Water Supplier Agencies") 
```

--- &twocol

**Questions 3 & 4: Have penalties on urban water suppliers affected residential water usage? Since June 2015, have urban water suppliers been meeting their required conservation standards?**

*** =left width:50%
```{r, echo=FALSE, fig.width=7, fig.height=3}

#Megan's NC plot

NCplot <- NCT %>%
  ggplot(aes(x=Penalties_Assessed, y=ResUse)) + geom_point(aes(color=Supplier_Name, size = 1)) + labs(title= "Northern California", x= "Number of Penalties Assessed", y= "Residential Water Use (Gallons-per-Capita-per-Day)", color = "Water Supplier \nAgency") +  
  theme(panel.background = element_rect(fill = "grey"),
        panel.grid.minor = element_line(linetype = "dotted"), 
    panel.background = element_rect(color = "black"),
        axis.title.x = element_text(size = rel(1.0)),
    axis.title.y = element_text(size = rel(.75)),
        axis.text = element_text(size = rel(.9)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.5)))

NCplot + guides(size=FALSE)
```


```{r, echo=FALSE, fig.width=6, fig.height=3}

# Megan's CV plot

CVplot <- CVT %>%
  ggplot(aes(x=Penalties_Assessed, y=ResUse)) + geom_point(aes(color=Supplier_Name, size =1)) + labs(title= "The Central Valley", x= "Number of Penalties Assessed", y= "Residential Water Use (Gallons-per-Capita-per-Day)", color = "Water Supplier \nAgency") +  
 theme(panel.background = element_rect(fill = "grey"),
    panel.background = element_rect(color = "black"),
    panel.grid.minor = element_line(linetype = "dotted"), 
    axis.title.x = element_text(size = rel(1.0)),
    axis.title.y = element_text(size = rel(.75)),
        axis.text = element_text(size = rel(.9)),
        legend.text = element_text(size = rel(1.0)),
        plot.title = element_text(size = rel(1.5)))

CVplot + guides(size=FALSE)

```
 
```{r, echo=FALSE, fig.width=7, fig.height=3}

#Megan's SC plot

#SCplot <- SCT %>%
  #ggplot(aes(x=Penalties_Assessed, y=ResUse)) + geom_point(aes(color=Supplier_Name, size=1)) + labs(title= "Southern California", x= "Number of Penalties Assessed", y= "Residential Water Use (Gallons-per-Capita-per-Day)", color = "Water Supplier \nAgency") +  theme(panel.background = element_rect(fill = "grey"),
    #panel.background = element_rect(color = "black"),
    #panel.grid.minor = element_line(linetype = "dotted"), 
    #axis.title.x = element_text(size = rel(1.0)),
    #axis.title.y = element_text(size = rel(.75)),
        #axis.text = element_text(size = rel(.9)),
        #legend.text = element_text(size = rel(1.0)),
        #plot.title = element_text(size = rel(1.5)))

#SCplot + guides(size=FALSE)

```

*** =right width:50%

```{r, echo=FALSE, fig.width=6.5, fig.height=7}

#Megan's last graph

ConP <- CONS %>%
  ggplot(aes(x=met, y=total, fill=met)) + geom_bar(stat="identity") + facet_wrap( ~ date, labeller = as_labeller(month_named), ncol=3, scales= "free_x") + scale_x_discrete(labels=c("No", "Yes")) + labs(title= "Water Supplier Compliance with Mandatory
Conservation Standards") +   ylab("Number of Water Supplier Agencies") + xlab("Compliance Met?") + 
scale_fill_manual("Compliance", values=c("firebrick4","dodgerblue4")) +
geom_text(aes(label=total), vjust=-.01, color='black', size=5) +  ylim(0,400) +
theme(panel.background =  element_rect(fill = "grey"),  
    panel.background = element_rect(color = "black"),  
    panel.grid.minor = element_line(linetype = "dotted"),   
    axis.title = element_text(size = rel(1.5)),
    axis.text = element_text(size = rel(.9)),
    legend.text = element_text(size = rel(1.0)),
    plot.title = element_text(size = rel(1.5)),
    legend.position="none",
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank()
) 

ConP 

```
